\documentclass{beamer}
\usepackage[latin1]{inputenc}
\usefonttheme[onlylarge]{structurebold}
\setbeamerfont*{frametitle}{size=\normalsize,series=\bfseries}
\setbeamertemplate{navigation symbols}{}
\usetheme{Goettingen}
\defbeamertemplate{itemize item}{checkbox}{\Square}
\defbeamertemplate{itemize item}{checked}{\Square\llap\CheckmarkBold}

\title[Lab Meeting I]{Lab Meeting I}
\author{Carles Boix}
\begin{document}

\begin{frame}
    \begin{center}
        {\large \textsc{Overall Goals}}
    \end{center}
        \small
    \begin{minipage}[ht!]{0.49\textwidth}
        \begin{itemize}
            \item Creation of a plasmid containing \emph{FAR1-22}/\emph{FAR1-WT} driven by \emph{GALpr}.
            \item Testing under a galactose and glucose gradient to determine level of activation required to stop cell cycle.
            \item Flow cytometry to measure DNA content after cell arrest.
        \end{itemize}
    \end{minipage}
    \hfill
    \begin{minipage}[ht!]{0.49\textwidth}
        \begin{itemize}
            \item Creation of a genomic strain containing \emph{FAR1-22}/\emph{FAR1-WT} driven by \emph{ZEV}$_{268}$\emph{pr}.
            \item Testing under a $\beta$-estradiol gradient mimicking the gal/glu gradient.
            \item Determination of appropriate conditions for both $\beta$-estradiol and blue light induction.
            \item Blue light controls.
        \end{itemize}
    \end{minipage}
\end{frame}

\begin{frame}
    \begin{center}
        {\large \textsc{Steps for Plasmid Construction}}
    \end{center}
        \begin{itemize}
            \item[$\boxtimes$]  Miniprep and digest pMM86
            \item[$\boxtimes$]  Miniprep pGAL-FAR1-22 (pTCN113)
            \item[$\boxtimes$]  PCR amplify FAR1-22 fragment
            \item[$\boxtimes$]  Colony PCR amplify FAR1-WT fragment
            \item[$\square$]  Digest both fragments
            \item[$\square$]  Gel extraction of fragments
            \item[$\square$]  Ligation 
            \item[$\square$] Transformation into bacteria
            \item[$\square$] Miniprep and sending to sequencing
            \item[$\square$] Transformation into yeast
        \end{itemize}
\end{frame}

\begin{frame}
    \begin{center}
        {\large \textsc{Steps for Genomic Strain Construction}}
    \end{center}
        \begin{itemize}
            \item[$\boxtimes$]  Miniprep pMM299 (ZEVpr)
            \item[$\boxtimes$]  Miniprep pCORE
            \item[$\boxtimes$]  Miniprep pGAL-FAR1-22 (pTCN113)
            \item[$\boxtimes$]  PCR amplify CORE fragment
            \item[$\boxtimes$]  PCR amplify FAR1-22 fragment
            \item[$\boxtimes$]  Colony PCR amplify FAR1-WT fragment
            \item[$\boxtimes$]  Colony PCR amplify ZEVpr fragment
            \item[$\boxminus$]  Transform ZEV yeast with CORE
            \item[$\square$] Transform ZEV+CORE with ZEVpr + FAR fragment
            \item[$\square$] Send to sequencing.
            \item[$\square$] Transform ZEV + FAR with the blue light plasmids
        \end{itemize}
\end{frame}

\begin{frame}
    \begin{center}
        {\large \textsc{Other steps in the near future:}}
    \end{center}
        \begin{itemize}
            \item[$\square$] Order sequencing primers.
            \item[$\square$] Build blue light rig.
            \item[$\square$] Transform ZEV strain w/ Blue light plasmids.
            \item[$\square$] Set up Galactose+Glucose stock.
            \item[$\square$] Plan for FACS experiment.
        \end{itemize}
\end{frame}


\end{document}
